Notes of Quantum Field Theory in a Nutshell

### 2016-08-30 QFT/Notes of QFT in a Nutshell/Notes of QFT in a Nutshell.tex
Inaugurating the new green function file, marking my first attempt at research level physics.

This section tries to replicate the previous section's procedure to
produce a repulsive force. It starts with the Maxwell's Lagrangian for
electromagnetism $\mathcal{L}=-\frac{1}{4} F_{\mu\nu}F^{\mu\nu}$.
However, the authors adds an additional mass term and let the mass
$m\to 0$ in the end. This is declared to be avoiding the complication of
gauge invariance. The result is surprisingly simple. We have:
\begin{align}
    D_{\nu\lambda}(k)&=\frac{-g_{\nu\lambda}+k_\nu k_\lambda/m^2}
        {k^2-m^2}
        = \frac{-G_{\nu\lambda}}{k^2-m^2}
        \nomenclature{$D_{\nu\lambda}$}
            {Propagator for massive spin $1$ field\nomrefpage}
    \nonumber\\
    W(J)&=\frac{1}{2} \int \frac{d^4k}{(2\pi)^4}
        J^\mu (k)^* \frac{1}{k^2-m^2+i\epsilon} J_\mu(k)
    \nonumber\\
    E&=\frac{1}{4\pi r}e^{-mr} 
\end{align}
where he defines 
$G_{\nu\lambda}\equiv g_{\nu\lambda}-\frac{k_\nu k_\lambda}{m^2}$.
This clearly represent the idea of repulsive Coulomb force.

@@

\paragraph{Bypassing Einstein}
% TODO stopped here.
\paragraph{Unclear Points} Marked in the book. Especially, where
in the calculatioin above shows that the field is of a spin $1$
or a spin $2$ meson?

>>>>

This section tries to replicate the previous section's procedure to
produce a repulsive force. It starts with the Maxwell's Lagrangian for
electromagnetism $\mathcal{L}=-\frac{1}{4} F_{\mu\nu}F^{\mu\nu}$.
However, the authors adds an additional mass term and let the mass
$m\to 0$ in the end. This is declared to be avoiding the complication of
gauge invariance. The result is surprisingly simple. We have:
\begin{align}
    D_{\nu\lambda}(k)&=\frac{-g_{\nu\lambda}+k_\nu k_\lambda/m^2}
        {k^2-m^2}
        = \frac{-G_{\nu\lambda}}{k^2-m^2}
        \nomenclature{$D_{\nu\lambda}$}
            {Propagator for massive spin $1$ field\nomrefpage}
    \nonumber\\
    W(J)&=\frac{1}{2} \int \frac{d^4k}{(2\pi)^4}
        J^\mu (k)^* \frac{1}{k^2-m^2+i\epsilon} J_\mu(k)
    \nonumber\\
    E&=\frac{1}{4\pi r}e^{-mr} 
\end{align}
where he defines 
$G_{\nu\lambda}\equiv g_{\nu\lambda}-\frac{k_\nu k_\lambda}{m^2}$.
\nomenclature{$G_{\nu\lambda}$}
    {$g_{\nu\lambda}-\frac{k_\nu k_\lambda}{m^2}$\nomrefpage}
This clearly represent the idea of repulsive Coulomb force.

@@

\paragraph{Bypassing Einstein}

The producedure here is almost identical to that of the previous chapter.
Here, two equations are sued to obtain the final result:
\begin{align}
    k^\mu \varepsilon^{(a)}{\mu\nu} &= 0\\
    g^{\mu\nu}\varepsilon^{(a)}{\mu\nu}&=0 \text{(traceless)}\\
\end{align}
result:
\begin{align}
    \sum_a \varepsilon^{(a)}_{\mu\nu}(k) \varepsilon^{(a)}(k)
        \varepsilon^{(a)}_{\lambda\sigma}(k)=
        (G_{\mu\lambda}G_{\nu\sigma}+G_{\mu\sigma}G_{\nu\lambda})
        -\frac{3}{2}G_{\mu\nu} G_{\lambda\sigma}
\end{align}
so that the propagator for a massive spin $2$ particle 
\nomenclature{$D_{\mu\nu,\lambda\sigma}(k)$}
{propagator for a massive spin $2$ particle\nomrefpage}
is:
\begin{align}
    D_{\mu\nu,\lambda\sigma}(k)=
    \frac{ (G_{\mu\lambda}G_{\nu\sigma}+G_{\mu\sigma}G_{\nu\lambda})
        -\frac{3}{2}G_{\mu\nu} G_{\lambda\sigma} }
        {k^2-m^2}
\end{align}

\paragraph{ Why we fall}

\paragraph{Unclear Points} Marked in the book.
